---
title: "Ego centric networks"
author: "Karthik Srinivasan"
date: "June 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)

```

## Why to use social network analysis

I refered to [this class notes](http://www.analytictech.com/e-net/pdwhandout.pdf) that wonderfully describes why social networks is useful. Also see [this notes](http://www.analytictech.com/mgt780/slides/egonet1.pdf) 

```{r, results = 'asis', echo = FALSE}
rmarkdownTable <- function(df){
  cat(paste(names(df), collapse = "|"))
  cat("\n")
  cat(paste(rep("-", ncol(df)), collapse = "|"))
  cat("\n")

  for(i in 1:nrow(df)){
    cat(paste(df[i,], collapse = "|"))
    cat("\n")
    }
invisible(NULL)
}

rmarkdownTable(head(iris))
```

## Concepts in SNA:

It will be worthwhile to read about the following sub-topics in Network analysis:

* Statistical properties of large networks
* Models of social network structure and evolution
* Link prediction
* Network community detection
* Diffusion
* Finding influential nodes in networks
* Networks with positive and negative ties

For multi-partite graphs, it is interesting to know:

* Simrank (too intensive)


## Ego-centric networks (ECN)

Some useful concepts in ECN are:

* Topological: 
  * Structural holes/ Brokerage
  * Embeddedness
* Compositional
  * Size
  * Alter attributes
  
* Assortivity  
   
Social network concepts that can be useful to theorize:

##### Homophily, heterophily and heterogenity
For example, if we are listing the diagnoses that are related to HIP (Hospital induced pneumonia), we can answers question as follows:
* Does the alters of HIP form groups that have domain interpretation (Coronoary diseases, Inflammatory conditions, etc) {Heterogenity}
* Ego (HIP) as structural holes, if there is no link between alters: Interpretation is autonomy, control and information (or HIP is an interim condition?)

Other properties that can be analyzed (pondered upon):
Network size, strength, reciprocity, (attribute differences), composition (how many gastro related diseases as compared to coronory)

## Conductance
## Prestige

# Apart from this

Also do the MDS and cluster visualization and regular community detection (for directed weigthed networks)

## Other links:

Super cool work by Katya 

http://kateto.net/networks-r-igraph
http://www.leonidzhukov.net/hse/2015/networks/
http://www.r-bloggers.com/summary-of-community-detection-algorithms-in-igraph-0-6/
http://stackoverflow.com/questions/9471906/what-are-the-differences-between-community-detection-algorithms-in-igraph

USe for assignment: 
http://www.biofabric.org/gallery/pages/SuperQuickBioFabric.html

# NN
https://inventingsituations.net/2014/11/09/kaggle-social-networks-competition/
https://www.kaggle.com/c/learning-social-circles
http://francescopochetti.com/community-detection-social-networks/

label.propagation.community(g)
leading.eigenvector.community(g)
spinglass.community(g)
edge.betweenness.community(g)
fastgreedy.community(g)
walktrap.community(g) based on random walk
Clique percolation (not in igraph but has code available
multilevel is same as lovain method (blondel) or fast community unfolding
## Leonid Zhukov lectures (HSE):

Cliques, K-plex (maximum k nodes is not connected to each of n nodes), K-core (at least k connections are connected to each n)

Communities:


Similarity based clustering
Clusterin/Community detection based on Link Similarity (single-linkage {most similar}, complete-linkage, mean similarity ) and then do agglomerative clustering based on similarity between groups
(KARATE example)

 - How to manually cut

Community detection using graph partitioning (look at graphs and cut the edges)

REQUIRED: Directed weighted overlapping community 
Then --> 

Modularity: (modularity score: fraction of edges wihtin cluster to expected fraction if edges were distributed at random)

--> Continue to use connected diagnoses as input variable for classification (no graph attribute)
 
 
