---
title: "Ego centric networks"
author: "Karthik Srinivasan"
date: "June 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)

```

## Why to use social network analysis

I refered to [this class notes](http://www.analytictech.com/e-net/pdwhandout.pdf) that wonderfully describes why social networks is useful. Also see [this notes](http://www.analytictech.com/mgt780/slides/egonet1.pdf) 

```{r, results = 'asis', echo = FALSE}
rmarkdownTable <- function(df){
  cat(paste(names(df), collapse = "|"))
  cat("\n")
  cat(paste(rep("-", ncol(df)), collapse = "|"))
  cat("\n")

  for(i in 1:nrow(df)){
    cat(paste(df[i,], collapse = "|"))
    cat("\n")
    }
invisible(NULL)
}

rmarkdownTable(head(iris))
```

## Ego-centric networks (ECN)

Some useful concepts in ECN are:

* Topological: 
  * Structural holes/ Brokerage
  * Embeddedness
* Compositional
  * Size
  * Alter attributes
  
Social network concepts that can be useful to theorize:

##### Homophily, heterophily and heterogenity
For example, if we are listing the diagnoses that are related to HIP (Hospital induced pneumonia), we can answers question as follows:
* Does the alters of HIP form groups that have domain interpretation (Coronoary diseases, Inflammatory conditions, etc) {Heterogenity}
* Ego (HIP) as structural holes, if there is no link between alters: Interpretation is autonomy, control and information (or HIP is an interim condition?)




